Graphical tests for coverage [@sailynoja2021graphical]

### 2021-11-29 docs/30-11-21_coverage/coverage.Rmd
80% there on passable slides. Need to add the new plots. Perhaps some actual discussion of the paper's contribution as well.

---
title: Graphical tests for coverage
subtitle: HIV Inference Lab Group Meeting
author: "Adam Howes"
date: "November 2021"
output:
  beamer_presentation:
    latex_engine: pdflatex
    highlight: haddock
    fig_width: 7
    fig_height: 3
    includes:
      in_header: preamble.tex
  slidy_presentation:
    highlight: haddock
bibliography: citations.bib
institute: Imperial College London
---

@@

@@

@@

@@

@@

@@

**Also note** that this isn't the only thing we care about.
If I tell you that the probability HIV prevalence is within $[0, 1]$ (no one to everyone) then you can't really fault my coverage, but also I'm not very useful.
Other thing we might care about is sharpness (saying more precise things).
Proper scoring rules assess these together, but I don't think they can be decomposed.

How could you assess this?

@@

@@

@@

>>>>

---
title: Graphical tests for coverage [@sailynoja2021graphical]
subtitle: HIV Inference Lab Group Meeting
author: "Adam Howes"
date: "November 2021"
output:
  beamer_presentation:
    latex_engine: pdflatex
    highlight: haddock
    fig_width: 7
    fig_height: 3
    includes:
      in_header: preamble.tex
  slidy_presentation:
    highlight: haddock
bibliography: citations.bib
institute: Imperial College London
---

```{r echo = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Caliration

@@

## Intervals

@@

## Confidence interval

@@

## Credible interval

@@

## Example of credible intervals

@@

## Expect to "be wrong" sometimes

@@

## Sharpness and SPSR

**Also note** that this isn't the only thing we care about.

If I tell you that the probability HIV prevalence is within $[0, 1]$ (no one to everyone) then you can't really fault my coverage, but also I'm not very useful.

Other thing we might care about is sharpness (saying more precise things).
Scoring rules assess these together.
Defining feature of (strictly) proper scoring rules is that they can't be gamed.

It would be nice is there was some type of decomposition along the lines of
$$
\text{score(forecast)} = \text{calibration(forecast)} + \text{sharpness(forecast)},
$$
but AFAIK that doesn't exist.

## Using raw data rather than truth

How can we assess the calibration of our credible intervals?

@@

## Nominal versus empirical

@@

## Example

Say that the nominal coverage is 90%:

| Analyst   | $n$ | Inside the CrI | Empirical coverage | Diagnosis |
| --------- | --- | -------------- | ------------------ | --------- |
| Hai Kon   | 28  | 27             | 96%                | Overconfident |
| Relan     | 28  | 21             | 75%                | Underconfident |

*Any resemblance to real people living or dead is purely coincidental.*

@@

```{r}
library(ggplot2)

ggplot() + 
  stat_function(fun = dnorm) +
  xlim(c(-3, 3)) +
  theme_void() +
  labs(title = "Posterior predictive distribution")
```

```{r}
ggplot() + 
  stat_function(fun = dnorm) +
  stat_function(fun = dnorm, xlim = c(-1.96, 1.96), geom = "area", alpha = 0.2) +
  xlim(c(-3, 3)) +
  theme_void() +
  labs(title = "Add a credible interval (equal-tailed)")
```

```{r}
ggplot() + 
  stat_function(fun = dnorm) +
  stat_function(fun = dnorm, xlim = c(-1.96, 1.96), geom = "area", alpha = 0.2) +
  geom_point(data = data.frame(x = 0.75, y = 0), aes(x = x, y = y), size = 5) +
  geom_label(data = data.frame(x = 0.75, y = 0.05, label = "Within interval"), aes(x = x, y = y, label = label)) +
  xlim(c(-3, 3)) +
  theme_void() +
  labs(title = "Suppose that this is the observation we get")
```

```{r}
ggplot() + 
  stat_function(fun = dnorm) +
  stat_function(fun = dnorm, xlim = c(-1.96, 1.96), geom = "area", alpha = 0.2) +
  geom_point(data = data.frame(x = 0.75, y = 0), aes(x = x, y = y), size = 5) +
  geom_label(data = data.frame(x = 0.75, y = 0.05, label = "Quantile: 0.674"), aes(x = x, y = y, label = label)) +
  xlim(c(-3, 3)) +
  theme_void() +
  labs(title = "Is it in the interval, yes or no, doesn't tell the full story.\nKnowing the quantile allows us to say if it's in any (equal-tailed) credible interval.")
```

Given a collection of posterior predictive quantile results $q_1, \ldots, q_n$, what can we do?

**Main point** if our forecast is calibrated then $q_i \sim \mathcal{U}[0, 1]$.

Hence "tests for discrete uniformity" [@sailynoja2021graphical].

Prior to seeing the paper, I was making some plots to check if the quantiles in my models looked uniform:

```{r}
knitr::include_graphics("twitter1.png")
```

```{r}
knitr::include_graphics("twitter2.png")
```
